\documentclass[aspectratio=169]{beamer}
%\usepackage{hyperref}
%\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{intersections}
\usepackage{siunitx}
\usepackage{pgfplots}
\pgfplotsset{compat=1.15}

% must add equation numbers in Part 1.
% rewrite sections.
% A better chronological description for blackbody.
% bit of part 2 and 3 are unfinished.
% some statements needs to be rechecked. 
% multi column did work with the correction. but it is still not showing part 3.
% graph is showing some errors in 239 which i could'nt understad due to lack of sleep.

\usepackage{multicol}

\newcommand{\highlight}[1]{\textbf{#1}}

\usetheme[progressbar=frametitle, numbering=none]{metropolis}
\setbeamercolor{background canvas}{bg=white}
\title{Spectrum of Blackbody}
\institute{Guided by V.H. Belvadi \\ Yuvaraja's College, Mysuru}
\author{Sudheendra B.R. \\ Suhas P.K. \\ Shahsank K.K.}
\date{}

\begin{document}

\begin{frame}[noframenumbering]
	\titlepage
\end{frame}

\begin{frame}[noframenumbering]{Overview}

		\tableofcontents[sections={1}] 
		
\end{frame}

\begin{frame}

		\tableofcontents[sections={2-3}]
		 
\end{frame}

\metroset{numbering = counter}

\section{Part 1}

\subsection{Introduction to the Black Body problem}

\begin{frame}{Introduction}

{\large An idealised object that can \highlight{absorb} and subsequently \highlight{emit}, all the radiation incident on it is called a \highlight{Blackbody}.}

\end{frame}

\subsection{Charged oscillators}
 
\subsection{Rayleigh's intensity function}

\begin{frame}{Rayleigh's law}

	\begin{itemize}
		
		\item Consider gaseous medium, in which we have a charged oscilator. \newline
		\item Due to random motion of the gaseous atoms, it often collides with the oscillator. \pause \newline
		\item As a result the gaseous atoms imparts some of it's kinetic energy to the oscillator.
		
	\end{itemize}
	
\end{frame}

\begin{frame}{Rayleigh's law}
	
	\begin{itemize}
	
		\item Mean kinetic energy acquired by the oscillator is, $\frac{1}{2}\,kT$. \newline
		\item And the total kinetic energy will be $ kT $. 
		
	\end{itemize}
		
\end{frame}

\begin{frame}{Rayleigh's law}

	\begin{itemize}

		%\item We have a charge which has some kinetic energy, \pause \newline
		%\item Means it \highlight{radiates} some of it's energy. \newline 
		\item Since the charge is radiating energy \highlight{the system cannot attain equilibrium}.
			
	\end{itemize}
	
\end{frame}

	
\begin{frame}{Rayleigh's law}

	\begin{itemize}
			
		%\item Since the charge is radiating energy to infinity,the system cannot attain equilibrium. \newline
		\item How do we tackle this situation? \pause \newline
		\item We confine the system.
		
	\end{itemize}
	
\end{frame}
	
		
\begin{frame}{Rayleigh's law}

	\begin{itemize}
			
		%\item The oscillator is kept   \newline
		\item Inner walls of the box is totally reflective.\newline
		\item After some time the system will attains \highlight{thermal equilibrium}
	\end{itemize}
	
\end{frame}
		
		
\begin{frame}{Rayleigh's law}
		
		So, the energy radiated  by the oscillator  per second can be given by, \newline
		{\large \[ \frac{1}{Q} = \frac{\left(\frac{dW}{dt}\right)}{\omega_0 W}\]}\newline
			{\small $Q$ is the radiation reaction. \\ $\omega_0$ is the natural frequency of vibration. \\ $W$ is the total energy content of the oscillator.} 
				
\end{frame}
	
		
\begin{frame}{Rayleigh's law}
		Also, we have 
		\[ \frac{1}{Q}= \frac{\gamma}{\omega_0} \]
			
			\begin{center}		
				{\small Where $\gamma$ is the dampping constant.}
			\end{center}
			
		Remember the mean energy of the oscillator is $kT$? for three degrees of freedom, it is $3kT$.
		
\end{frame}


\begin{frame}{Rayleigh's law}

	 \begin{center}
	 
	 	{\large Average energy loss due to radiation is given by,} \newline
	 	
	  \end{center} 
	  
	 {\large \[ \boxed{\left<\frac{dW}{dt}\right> = \gamma kT}\]}	 		

\end{frame}
		
\begin{frame}{Rayleigh's law}
	
	\begin{itemize}
		
		\item Let, $ \mathbf{I}(\omega)d\omega $ be the incident light energy with in a frequeny range $d\omega$. \newline
		\item Assuming all the radiation which falls on a \textit{cross section} '$\sigma_s$' is absorbed completely, \newline
		\item Scattered light must be the product of $ \mathbf{I}(\omega)d\omega $ and $ \sigma_s $.

	\end{itemize}
	
\end{frame}
			
\begin{frame}{Rayleigh's law}
	\begin{center}
		Expression for the cross section is given by,
	\end{center}
	
	{\large \[ \sigma_s = \frac{8\pi {r_0}^{2}}{3} \left[ \frac{\omega^{4}}{(\omega^2-{\omega_0}^{2})^2+\gamma^2 \omega^2}\right] \]}\newline
	When $ \omega\,=\,\omega_0 $, \newline 		
	{\large \[ \sigma_s = \frac{2\pi {r_0}^{2}{3} \omega_0^{2}}{3(\omega-\omega_0)^2+\dfrac{\gamma^2}{4}} \]}
	
\end{frame}
				
\begin{frame}{Rayleigh's law}

	\[ \frac{dW_s}{dt}=\int_0^{\infty}{\mathbf{I}(\omega)\,\sigma_s \, d\omega} = \int_0^{\infty}{\frac{2\pi {r_0}^{2} \omega_0^{2} \, \mathbf{I}(\omega)\, d\omega}{3 \left[ (\omega-\omega_0)^2+\dfrac{\gamma^2}{4} \right] }} \] \newline

	since we're considering the equilibrium condition ($\omega =\omega_0 $), equation reduces to,
	\[ \frac{dW_s}{dt}= \frac{2}{3}\pi {r_0}^{2} \omega_0^{2} \, \mathbf{I}(\omega_0) \int_{-\infty}^{\infty}{\frac{d\omega}{(\omega-\omega_0)^2+{\left(  \dfrac{\gamma}{2} \right)}^{2}}}  \]

\end{frame}

\begin{frame}{Rayleigh's law}\vspace{1cm}

	Since the integral reduces to arctan function we get, $\frac{2\pi}{\gamma}$. and as 
		\[\frac{dW_s}{dt}= \frac{dW}{dt}\],
		% we get the intensity 
		\[\mathbf{I}(\omega)=\frac{9\gamma^2\,kT}{4\pi^2 r_0^2\omega_0^2} \] 
	The value of $\gamma$ wa found to be equal to,
		\[ frac{2}{3} \frac{r_0 \omega_0^2}{c} \]
	
\end{frame}

\begin{frame}{Rayleigh's law}
	% {\large the intansity distribution function \[\mathbf{I}(\omega) is, }
	 \[\mathbf{I}(\omega)=\frac{\omega^2\,kT}{\pi^2 c^2} \] 
\end{frame}

\begin{frame}[fragile]{Graph}
	\begin{tikzpicture}[samples=100, scale=1.5]
		\draw[->,thick] {(0,0) -- (0,6)};
		\draw[->,thin] {(0,0) -- (7,0)};
    \begin{axis}[
        xlabel={$\omega$ [\si{\hertz}]},
        ylabel={$\rho (\omega; T)$ [\si{\joule\per\cubic\meter}]},
        no markers,
        domain=0.1:40,
		  axis line style={draw=none},
		  tick style={draw=none},
        style={thick}]

       \addplot [forget plot,name path=B,samples=2] {0};

    \pgfplotsinvokeforeach{3500, 4500, 5500, 6500}
    {
        \addplot+ 
        {(x^3)/((pi^2)*(exp(2000*x/(#1))-1))};
        \addlegendentryexpanded{$T = #1 [\si{\kelvin}]$}
    }

    \end{axis}
    
    \end{tikzpicture}

\end{frame}

				
\subsection{The Ultra-Violet catastropy} 

\subsection{Plank's emphirical formula}
\begin{frame}{}

	\begin{itemize}
		%%%Photo of Planck is needed.	
		\item Theoretical proof was needed for to explain the obtained experimental results. \newline
		
		
	\end{itemize}
	
\end{frame}

\begin{frame}{}

	\begin{itemize}

		\item The harmonic oscillator can take up energies only in the multiples of $ \mathbf{\hbar \omega} $.  \newline
		\item The probability of occupying an energy level \textbf{E} is {\large $\mathbf{P(E)} = \alpha e^{\frac{-\hbar \omega}{kT}}$} . 
	\end{itemize}
	
\end{frame}

\begin{frame}

	\begin{itemize}
		\item The number of oscillators in ground state is $ N_0 $ . \newline
		\item The number of oscillator in first state is $ N_1 = N_0  e^{-\hbar \omega / {kT}} . $ \vspace{0.5cm}
		\item Then $ N_n = N_0 x^n $ , where $ x = e^{-\hbar \omega / {kT}} $
	\end{itemize}
\end{frame}

\begin{frame}
	\begin{itemize}
	\item The energy in the ground state is zero. \newline
	\item The energy in the first state is $ N_1 \hbar \omega $ or $ N_0 \hbar \omega x $ \newline
	\item Total energy is given by \[ E_ \left(total \right) = N_0 \hbar \omega ( 0 + x + 2 x^2 + \cdots ) \] 
	\end{itemize}
\end{frame}
\section{Part 2}

\subsection{Intensity of a Black Body spectrum and the problem}

\begin{frame}{}

	\begin{itemize}

		\item The intensity of radiation for frequency $\omega$ is given by \[I(\omega)d\omega = \frac{\hbar \omega^3 d\omega}{ \pi^2 c^2 \left(e^{\frac{\hbar \omega}{kT}}-1 \right) } \] \newline
		\item Planck considered that the matter was quantized and not light. \newline
		\item Einstein came up with an alternate idea to solve Black body problem.
		 
	\end{itemize}
	
\end{frame}

\subsection{Einstein's work on Black Bodies}

\begin{frame}{}

	\begin{itemize}

		\item Einstein considered that even the light was quantized, by taking that light is actually photons with energy $\hbar \omega$   \newline
		\item a pic is needed.

	\end{itemize}
	
\end{frame}

\begin{frame}{}

	\begin{itemize}
	
		\item Einstein assumed that Planck's formula was right. \newline
		\item Consider two energy levels , say , the $n^{th}$ level and $m^{th}$ level. \newline
		\item A light of certain frequency is incident on atom and by absorbing a photon, transition from state n to state m occurs. 
 
	\end{itemize}
	
\end{frame}

\begin{frame}

	\begin{itemize}

		\item The probability of the transition is proportional to intensity of the light. \newline
		\item The proportionality constant is $B_{nm}$ and mathematically can be written as,
		
	\end{itemize}
		
			\begin{equation}
					 R_{n \to m} = N_{n} B_{nm} I(\omega) 	 
			\end{equation} 
						
\end{frame}

\begin{frame}{}

	\begin{itemize}

		\item Einstein considers that there are two types of emissions that take place in an atom. \newline
		\item Spontaneous emission. \newline
		\item Stimulated emission.
		
	\end{itemize}
	
\end{frame}

\begin{frame}{}

	\begin{itemize}
	
		\item The combined mathematical expression is,
		
	\end{itemize}
	
			\begin{equation}
					 R_{m \to n} = N_{m} [A_{mn} + B_{mn} I(\omega)] 
			\end{equation} 
	
\end{frame}

\begin{frame}{}

	\begin{itemize}

		\item At thermal equilibrium, the number of atoms going to higher energy level ,ust be equal to the number of atoms coming to 					  lower energy state. \newline	
		\item The ratio of $ N_{m} $ to $ N_{n} $ is given by $ e^{\frac{-\hbar \omega}{kT}} $  \newline
 
	\end{itemize}
	
\end{frame}

\begin{frame}{}

	\begin{itemize}

		\item At thermal equilibrium both $ R_{n \to m} $ and $ R_{m \to n} $ are equal.  \newline
		\item $ N_{n} B_{nm} I(\omega) = N_{m} [A_{mn} + B_{mn} I(\omega)] $ \newline
		\item On dividing the previous equation by $ N_{m} $ we get, 
		
	\end{itemize}
	
\end{frame}

\begin{frame}{}

	\begin{itemize}

		\item $ B_{nm} I(\omega) e^{\frac{\hbar \omega}{kT}} = A_{mn} + B_{mn} I(\omega) $ \newline
		\item So the equation that Einsteim got for intensity of radiation for frequency is 
		
	\end{itemize}
	
		\begin{equation}
				 I(\omega) = \frac{A_{mn}}{B_{nm} e^{\frac{\hbar \omega}{kT}} - B_{mn} }
		\end{equation}
		
\end{frame}

\begin{frame}{}

	\begin{itemize}

		\item Since Einstein considered that the formula given by Planck was correct, we should get , \newline
		\item  $ B_{nm} = B_{mn} $  and also
		
			\begin{flushleft} % It's not looking good.
			
				 \[\frac{A_{mn}}{B_{nm}} = \frac{\hbar \omega^3 d\omega}{ \pi^2 c^2} \] 

			\end{flushleft}
			
	\end{itemize}
	
\end{frame}

\begin{frame}{}

	{\Large This is how Einstein rederived Planck's formula from a quantum mechanical viewpoint.}
		
\end{frame}

\section{Part 3}

\begin{frame}{}

	\begin{itemize}

		\item \textbf{P} = probability\newline
		\item $ \phi $ = Probability amplitude \newline
		\item \textbf{P} = $ \,\Bigr\rvert\,\phi \,\Bigr\rvert\,^{2} $ 
		
	\end{itemize}
	
\end{frame}

\begin{frame}{}

	\begin{itemize}

		\item $ \phi $ = $ \phi_{1} + \phi_{2} $ \newline
		\item \textbf{P} = $ \,\Bigr\rvert\,\phi_{1} + \phi_{2} \,\Bigr\rvert\,^{2} $ 
	
	\end{itemize}
	
\end{frame}

\begin{frame}{Case A}

	\begin{itemize}
		\item Detector 1 is set to detect only $ \alpha $ particles and Dectector 2 is set to detect only oxygen atoms.\newline
		\item Probability amplitude of the scattering is given as $ f(\theta)$ when they are at an angle $\theta$.\newline
		\item The probability of this event = $ \,\Bigr\rvert\,f(\theta) \,\Bigr\rvert\,^{2} $
	\end{itemize}
		
\end{frame}


\begin{frame}{Case B}

	\begin{itemize}
	
		\item Set up the dectectors such that the detectors would dectect either $\alpha$ particle or oxygen atom.\newline
		\item We will not distinguish which particle is which entering the detector.\newline
		\item This means that if oxygen atom in position $\theta$ , then
		$\alpha$ particle on the opposite side is at an angle $\pi-\theta$.
		
	\end{itemize}
	
\end{frame}

\begin{frame}

	\begin{itemize}
	
		\item Probability amplitude of oxygen atom = $f(\pi-\theta)$ \newline
		\item Probability amplitude of $\alpha$ particle = $f(\theta)$ \newline
		\item The probability of a particle 
		being detected at detector 1 = $ \,\Bigr\rvert\,f(\theta) \,\Bigr\rvert\,^{2} $ + $ \,\Bigr\rvert\,f(\pi - \theta) \,\Bigr\rvert\,^{2} $
		
 	\end{itemize}
 	
\end{frame}

\begin{frame}{}

	\begin{itemize}

\item Consider if both are $ \alpha $ particles, \newline
\item Then we would not know which particle entered the detector, so the total probability changes to,  \newline
\item  The probability of a $ \alpha $ particle 
		being detected at detector 1 = $ \,\Bigr\rvert\,f(\theta) + f(\pi - \theta) \,\Bigr\rvert\,^{2} $
		
	\end{itemize}
	
\end{frame}

\begin{frame}

	\begin{itemize}

		\item If  $\theta = \dfrac{\pi}{2}$,  then applying this to the expression  $\,\Bigr\rvert\,f(\theta)+f(\pi-\theta)\,\Bigr\rvert\,^{2}$ we get, \newline
		\item Probability = $4 \,\Bigr\rvert\,f\left(\dfrac{\pi}{2}\right) \,\Bigr\rvert\,^{2}$ , if the particles are indistinguishible.
		
	\end{itemize}
	
\end{frame}

\begin{frame}{}

	\begin{itemize}

		\item Suppose the particles were distinguishible, then the probability for $\theta = \dfrac{\pi}{2}$ when applied for $ \,\Bigr\rvert\,f(\theta) \,\Bigr\rvert\,^{2} $ + $ \,\Bigr\rvert\,f(\pi - \theta) \,\Bigr\rvert\,^{2} $ is given by, \newline
		\item Probability = $2 \,\Bigr\rvert\, f\left(\dfrac{\pi}{2}\right) \,\Bigr\rvert ^{2}$ \newline 
		\item This shows that the probability gets doubled for indistinguishible particles.

	\end{itemize}
	
\end{frame}

\begin{frame}

	\begin{itemize}
	
		\item \textit{Can we apply the same logicto the electron-electron scattering ? }\newline
		\item \textit{OBSERVATION} : " When we have situation in which the identity of the electron which is arriving at a point is echanged with anothe one , the new amplitude interfere with old one with an opposite phase." \newline
		\item In electrons case , the interfering amplitude for exchange interfere with a negative sign. \newline
		Probability for electron = $\,\Bigr\rvert\,f(\theta)-f(\pi-\theta)\,\Bigr\rvert\,^{2}$
		
		 \end{itemize}
		 
\end{frame}

\begin{frame}

	SPIN PROBABILITY TABLE
	
\end{frame}

\begin{frame}{Identical Particles}
	
		{\large \textbf{Identical particles}\,, also called \textbf{indistinguishable particle}\,, are particles that cannot be distinguished from one another.}
		
\end{frame}

\begin{frame}{Identical - Indistinguishable Particles}

	\begin{itemize}
	
		\item Consider particle 'a' and particle 'b'. \newline
		\item Let the two particle collide and get sactttered in two different directions say '1' and '2' over a surface element $ds_{1}$ and $ds_{2}$ of the detector respectively. \newline
		\item If the particles are indistinguishable then the amplitudes of these process will add up. \newline
		\item Probability that the two particles arrive at $ds_{1}$ and $ds_{2}$ is \newline
		$\,\Bigr\rvert\,<1|a><2|b> + <2|a><1|b>\,\Bigr\rvert\,^{2} ds_{1} ds_{2}$
		
	\end{itemize}
	
\end{frame}

\begin{frame}

	\begin{itemize}
	
		\item Integrating over the area of the detector ,  if we let $ds_{1}$ and $ds_{2}$ rangr over the whole area $(\vartriangle S)$ , we could count each part of the area twice since the expression $\,\Bigr\rvert\,<1|a><2|b> + <2|a><1|b>\,\Bigr\rvert\,^{2} ds_{1} ds_{2}$ contains everything that can happen with any pair of surface elements $ds_{1}$ and $ds_{2}$. \newline
		\item $ Probability_{BOSE} = \dfrac{ \left(4\,\Bigr\rvert a \,\Bigr\rvert^{2} \,\Bigr\rvert b \,\Bigr\rvert^{2}\right)}{2} \left(\vartriangle S\right)$ \newline
		\item This is just twice what we got the probability for distinguished particles. 

	\end{itemize}
	
\end{frame}

\begin{frame}{State with n Bose particle}

	\begin{itemize}
	
		\item Consider n particles say a, b, c... scattered in n direction say 1, 2, 3 ... \newline
		\item Probability that each particle acting alone would go into an element of the surface ds of the detector is $\,\Bigr\rvert < >\,\Bigr\rvert^{2} ds$. 
		
	\end{itemize}
	
\end{frame} 

\begin{frame}

	\begin{itemize}
	
		\item \textbf{Assumption} :All particles are distinguishable. \newline
		\item Probability that n particles will be counted together in n different surface elements = $\,\Bigr\rvert a_{1}b_{2}c_{3}... \,\Bigr\rvert^{2}ds_{1}ds_{2}...$ \newline
		\item If the amplitude does not depend on where ds is located in the detector , then the \newline
		$Probability = \left(\,\Bigr\rvert a \,\Bigr\rvert^{2}\,\Bigr\rvert b \,\Bigr\rvert^{2}...\right)(ds_{1}ds_{2}...)$
		
	\end{itemize}
	
\end{frame} 

\begin{frame}

	\begin{itemize}
	
		\item Integrating each dS over the surface $\vartriangle S$ of the dectector \newline 
		$(P_{n})_{different} = \left(\,\Bigr\rvert a \,\Bigr\rvert^{2}\,\Bigr\rvert b \,\Bigr\rvert^{2}...\right)(\vartriangle S)^{n}$ \newline
		\item Now suppose that all the particle are Bose particles.
		\item For n particles, there are n! different , but indistinguishable  possibilities for which we must add the amplitudes.
		
	\end{itemize}
	
\end{frame}

\begin{frame}

	\begin{itemize}
	
	\item Probability that n particles will be counted on the n surface elements is given by \newline $Probability = \left(\,\Bigr\rvert a_{1}b_{2}c_{3}... + a_{1}b_{3}c_{2}... \,\Bigr\rvert^{2}\right)(ds_{1}ds_{2}...)$
	\item $Probability = \left(\,\Bigr\rvert n!abc... \,\Bigr\rvert^{2}\right)(ds_{1}ds_{2}...)$
	\item Integrate each ds over the area $\vartriangle S$ of the detector \newline
	$(P_{n})_{BOSE} = n!\left(\,\Bigr\rvert abc... \,\Bigr\rvert^{2}\right)(\vartriangle S)^{n}$
	
	\end{itemize}

\end{frame}

\begin{frame}

	\begin{itemize}
	
	\item Compareing the probability when the particles are distinguishable and indistinguishable \newline
	$(P_{n})_{BOSE} = n!\left(\,\Bigr\rvert abc... \,\Bigr\rvert^{2}\right)(\vartriangle S)^{n}$ \newline
	$(P_{n})_{different} = \left(\,\Bigr\rvert a \,\Bigr\rvert^{2}\,\Bigr\rvert b \,\Bigr\rvert^{2}...\right)(\vartriangle S)^{n}$ 
	\item $(P_{n})_{BOSE} = n!(P_{n})_{different}$
	
	\end{itemize}
	
\end{frame}

\begin{frame}

	
	{\large	What is the probability that a Bose particle will go into particular state when there are already n particles present ?}
		
\end{frame}

\begin{frame}{Emission and Absorption of photons}

	\begin{itemize}
	
		\item When the light is emitted, a photon is "created".\newline
		\item Consider that there are some atom emitting n photons. \newline
		\item \textit{OBSERVATION} : The probability that an atom will wmit a photon into a particular final state is increased by the factor (n+1) if there are already n photons in that state.
		
	\end{itemize}
	
\end{frame}

\begin{frame}{The Blackbody Spectrum}

\end{frame}
\begin{frame}{The Blackbody Spectrum}
	\begin{itemize}
	 \item For each light frequency $\omega$, there are certain N number of atoms which have two energy states separated, given by the equation $E = \omega\hslash$. \newline
	 \item Let $N_{e}$ and $N_{g}$ be the average numbers of atoms that are in excited state and ground state. \newline
	 \item In thermal equilibrium at temperature T, from statistical mechanics \newline
	 %$\dfrac{N_{e}}{N_{g}} = a^{\left(\dfrac{-\vartriangleE}{\omega\hslash}\right)}$  \newline
	\item NOTE: Each atom in the ground stae can absorb a photon and go into the excited state and each atom in the excited state can emit a photon and go to the ground state.
	\end{itemize}
\end{frame} 

\begin{frame}
	\begin{itemize}
		\item At equilibrium, the rate of these two process must be equal. \newline
		\item Rate is proportional to the probability of the event and the number of atoms present.\newline
		\item $\overline{n}$ is the average number of photons present in a given state with the frequency $\omega$
	\end{itemize}
\end{frame}

\begin{frame}
	\begin{itemize}
		\item The absorption rate from the state is $N_{g}\overline{n}\,\Bigr\rvert\,a\,\Bigr\rvert\,^{2}$ , and the emission rate into that state is $N_{e}(\overline{n}+1)\,\Bigr\rvert\,a\,\Bigr\rvert\,^{2}$.
		\item At equilibrium  $N_{g}\overline{n}\,\Bigr\rvert\,a\,\Bigr\rvert\,^{2} = N_{e}(\overline{n}+1)\,\Bigr\rvert\,a\,\Bigr\rvert\,^{2}$
	\end{itemize}
\end{frame}

\subsection{Amplitude-based descriptiom of identical particles}

\subsection{n Boson systems}

\subsection{Probability based emission and absorption of Black Bodies}


\end{document}


